Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

### Why we chose to look into Education to explain Entrepreneurship

@@

More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities. Yet, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.

@@

In 2010, 
Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.

@@

>>>>

### Why we chose to look into Education to explain Entrepreneurship - What has been done

@@

More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors. As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities. In 2010, Freytag and Thurik ????? 2010 VERSION MAINBIB ????? have also studied determinants of entrepreneurship in a cross-country setting and pointed at cultural features. Their results showed that "country specific (cultural) variables seem to explain the preference for entrepreneurship" and self-employment. Yet, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.

@@

???????????????????????????????????????????????????????????????????????????

@@

????????????????????????????????????????????????????????????????????????????????????

### What we intend to do
